\vskip-0.6in LOBBYING AND LEGISLATIVE UNCERTAINTY

### 2016-02-15 draft.tex
write prop:asym and modify evidence section

\begin{proposition}
  When Vote Buyer $B$ pays bribes to exactly one legislator, ... can be any one, not necessarily ideologically closest.
	\label{prop:1NNB}
\end{proposition}
In contrast to models with no uncertainty about legislators' ideological positions, here we have an anti-result that the vote buyers do not necessarily bribe those who are ideologically most aligned with themselves. The non-negativity constraint often rules out bribing the most friendly legislator(s) because she/they don't contribute very much to the overall probability of winning the issue.

@@

\begin{proposition}
  test
\end{proposition}
Very low, very high uncertainty gets lowest payments, middle uncertainty gets most (Figure \ref{fig:g1}.

@@

\textcolor{blue}{Figure~\ref{fig:br} displays the relationship between lobbying effort and legislators' support for one bill of interest, the Korea-U.S. Free Trade agreement, or KORUS. The vertical axis represents the predicted probability that a legislator would vote ``yes'' on the agreement, and the horizontal axis shows the monetary contributions to each legislator by lobbies who supported the passage of KORUS minus the contributions from lobbies opposing the agreement. The solid vertical red line indicates the average net contribution in the sample, and the dashed lines a one-standard deviation increase/decrease from that sample mean. The data indicate that exporting industries are more likely to exert lobbying effort to enlist the support of additional legislators (extensive margin) rather than secure stronger support from a given set of legislators (intensive margin), as well as that there are decreasing returns to lobbying effort. To generate these results,  we regressed a legislator's vote on his/her estimated ideal point as well as partisanship using a probit specification. Then we fitted a second-order polynomial to the predicted probabilities generated by the probit regression. The contribution data for both this and the following figure was obtained from Maplight.}

\textcolor{blue}{Figure~\ref{fig:g1} displays the relationship between the unpredictability of legislators' voting behavior and lobbying effort. The vertical axis represents the predicted net contributions to members of the U.S. House of Representatives in 2012, and the horizontal axis shows the unpredictability of legislator's voting behavior measured using the 95$\%$ posterior confidence intervals of their ideal points estimated using Bayesian Markov chain simulation to scale all roll call votes taken in the 112th Congress (more details on the methodology below). The solid vertical red line indicates the average uncertainty in the sample, and the vertical dashed red lines indicate increases/decreases of one-standard deviation from the average. The horizontal dashed green line indicates the predicted net payment in the sample. The data show a very strong relationship between uncertainty at the level of the individual legislator and campaign contributions. To generate these results, we fitted a second-order polynomial to the data, and used monetary contributions to each legislator by lobbies who supported the passage of KORUS minus the contributions from lobbies opposing the agreement.}

@@

>>>>

\begin{proposition}
  When Vote Buyer $B$ pays bribes to exactly one legislator, it may be any one of the three legislators depending on the bias parameter $\al$.
	\label{prop:1NNB}
\end{proposition}
In contrast to models with no uncertainty about legislators' ideological positions, here we have an anti-result that the vote buyers do not necessarily bribe those who are ideologically most aligned with themselves. The non-negativity constraint often rules out bribing the most friendly legislator(s) because she/they don't contribute very much to the overall probability of winning the issue.

@@

\begin{proposition}
  When there is no bias in the positions of the legislators ($\al =0$), the bribes of legislators whose ideal points are at the median in terms of uncertainty receive the highest relative bribes. (conjecture)
	\label{prop:asym}
\end{proposition}
In numerical examples, this pattern holds strongly. By `relative,' we mean that the bribes are scaled up relative to the equal gross position that occurs when uncertainty is symmetric. We also see that the bribes for legislators whose ideal points are more uncertain are scaled down while the bribes of legislators whose ideal points are less uncertain are scaled up, modulo relative position. That is, there is some effect of being more friendly versus less friendly, as the cumulative density that the legislator will vote in the vote buyer's favor changes in opposite directions when uncertainty rises depending on whether the legislator is friendly or unfriendly. This accords well with the finding in Figure \ref{fig:g1} that those legislators with very low and very high uncertainty gets the lowest payments, while those with more average levels of uncertainty receive the most.

@@

Figure~\ref{fig:br} displays the relationship between lobbying effort and legislators' support for one bill of interest, the Korea-U.S. Free Trade agreement, or KORUS. The vertical axis represents the predicted probability that a legislator would vote ``yes'' on the agreement, and the horizontal axis shows the monetary contributions to each legislator by lobbies who supported the passage of KORUS minus the contributions from lobbies opposing the agreement. The solid vertical red line indicates the average net contribution in the sample, and the dashed lines a one-standard deviation increase/decrease from that sample mean. To generate these results,  we regressed a legislator's vote on his/her estimated ideal point as well as partisanship using a probit specification. Then we fitted a second-order polynomial to the predicted probabilities generated by the probit regression. The contribution data for both this and the following figure was obtained from Maplight. The data indicate that exporting industries were more likely to exert lobbying effort to enlist the support of additional, moderate legislators rather than secure stronger support from those most aligned with their interests. This accords well with Proposition~\ref{prop:1NNB}.

Figure~\ref{fig:g1} displays the relationship between the unpredictability of legislators' voting behavior and lobbying effort. The vertical axis represents the predicted net contributions to members of the U.S. House of Representatives in 2012, and the horizontal axis shows the unpredictability of legislator's voting behavior measured using the 95$\%$ posterior confidence intervals of their ideal points estimated using Bayesian Markov chain simulation to scale all roll call votes taken in the 112th Congress. The solid vertical red line indicates the average uncertainty in the sample, and the vertical dashed red lines indicate increases/decreases of one-standard deviation from the average. The horizontal dashed green line indicates the predicted net payment in the sample. To generate these results, we fitted a second-order polynomial to the data, and used monetary contributions to each legislator by lobbies who supported the passage of KORUS minus the contributions from lobbies opposing the agreement. The data show a very strong relationship between uncertainty at the level of the individual legislator and campaign contributions as predicted by Proposition~\ref{prop:asym}.

@@

\vskip.3in
\noindent \textbf{\hypertarget{Pr_1NNB}{Proof of Proposition~\ref{prop:1NNB}}}: \\
When Vote Buyer B bribes just one legislator, two non-negativity constraints are binding and only one first order conditions holds with equality with the Lagrange multiplier equaling zero. We can easily solve this first order condition to find the value of the bribe. What determines which legislator is bribed is which legislator's ideal point distribution has the most mass near zero, as moving this individual has the greatest impact on total probability of winning the issue.
